---
title: "Gov 50 Final Project"
author: "Wakiko Ohira"
description: "My final project"
output:
  distill::distill_article:
    self_contained: false
---
```{r}
load("/Users/wakiko/Mac Google Drive/Harvard/Courses/Gov 50_Blackwell/afrobarometer2016.RData")
```

```{r}
library(haven)
round8 <- read_sav("data/afrobarometer_release-dataset_merge-34ctry_r8_en_2023-03-01.sav")
round2 <- read_sav("data/merged_r2_data.sav")
round7 <- read_sav("data/r7_merged_data_34ctry.release.sav")
```

```{r}
#remotes::install_github("xmarquez/democracyData")
library(democracyData)
polity <- democracyData::polity5
```


## Project thoughts

I this study, I plan to examine the relationship between local citizens' trust in local government and their trust in traditional authorities in Sub-Saharan Africa. Traditional authorities, such as kingdoms and chiefdoms, are essential actors in local governance, and their roles vary from land allocation, customary arbitration, and provision of local public goods and services. In my previous study, I qualitatively examined the case of Uganda. In Uganda, the less citizens trust in local government, the more they trust in traditional authorities. My qualitative analysis showed that, because the central government instrumentalized local governments for the purpose of power consolidation, it greatly undermined local governments' capability to provide public goods and services. Local citizens are disappointed with both the central government and local governments, and their expectations of the kingdoms increased to be an alternative player in local governance. Using this qualitative study as a case, I hypothesize that, in more democratic countries in Sub-Saharan Africa, people's trust in local government and their trust in traditional authorities correlate positively, and in semi-authoritarian countries like Uganda, people's trust in local government and their trust in traditional authorities have negative correlation. I use the data from Afrobarometer (Round 2 and Round 8) to examine how much people's trust in local government increased or decreased over the past 20 years. I do the same analysis for how much people's trust in traditional authorities increased or decreased over the past 20 years. I conduct these analysis both at the individual level and the country level. Then, I combine the results with the data from polity, which shows the level of democracy, to test the hypothesis. 

```{r}
library(dplyr)

R2_trust <-
  round2 |>
  select(c(country, q43e, q43k)) |>
  mutate(round = "r2")

R8_trust <-
  round8 |>
  select(c(COUNTRY, Q41D, Q41K)) 

R7_trust <-
  round7 |>
  select(c(COUNTRY, Q43D, Q43J))　|>
  mutate(round = "r7")

```

```{r}
names(R2_trust) 
names(R8_trust)
names(R7_trust)

R2_trust <-
  rename(R2_trust,
         LG_trust = q43e,
         TL_trust = q43k)

R8_trust <-
  rename(R8_trust,
         country = COUNTRY,
         LG_trust = Q41D,
         TL_trust = Q41K)

R7_trust <-
  rename(R7_trust,
         country = COUNTRY,
         LG_trust = Q43D,
         TL_trust = Q43J)
```

```{r}
## another method 
R2_trust$country_name <- NA_character_
R2_trust$country_name[R2_trust$country==1] <- "Botswana"
R2_trust$country_name[R2_trust$country==2] <- "Ghana"
R2_trust$country_name[R2_trust$country==3] <- "Lesotho"
R2_trust$country_name[R2_trust$country==4] <- "Malawi"
R2_trust$country_name[R2_trust$country==5] <- "Mali"
R2_trust$country_name[R2_trust$country==6] <- "Namibia"
R2_trust$country_name[R2_trust$country==7] <- "Nigeria"
R2_trust$country_name[R2_trust$country==8] <- "South Africa"
R2_trust$country_name[R2_trust$country==9] <- "Tanzania"
R2_trust$country_name[R2_trust$country==10] <- "Uganda"
R2_trust$country_name[R2_trust$country==11] <- "Zambia"
R2_trust$country_name[R2_trust$country==12] <- "Zimbabwe"
R2_trust$country_name[R2_trust$country==13] <- "Cape Verde"
R2_trust$country_name[R2_trust$country==14] <- "Kenya"
R2_trust$country_name[R2_trust$country==15] <- "Mozambique"
R2_trust$country_name[R2_trust$country==16] <- "Senegal"
```

```{r}
R7_trust$country_name <- NA_character_
R7_trust$country_name[R7_trust$country==1] <- "Benin"
R7_trust$country_name[R7_trust$country==2] <- "Botswana"
R7_trust$country_name[R7_trust$country==3] <- "Brukina Faso"
R7_trust$country_name[R7_trust$country==4] <- "Cabo Verde"
R7_trust$country_name[R7_trust$country==5] <- "Cameroon"
R7_trust$country_name[R7_trust$country==6] <- "Côte d'Ivoire"
R7_trust$country_name[R7_trust$country==7] <- "eSwatini"
R7_trust$country_name[R7_trust$country==8] <- "Gabon"
R7_trust$country_name[R7_trust$country==9] <- "Gambia"
R7_trust$country_name[R7_trust$country==10] <- "Ghana"
R7_trust$country_name[R7_trust$country==11] <- "Guinea"
R7_trust$country_name[R7_trust$country==12] <- "Kenya"
R7_trust$country_name[R7_trust$country==13] <- "Lesotho"
R7_trust$country_name[R7_trust$country==14] <- "Liberia"
R7_trust$country_name[R7_trust$country==15] <- "Madagascar"
R7_trust$country_name[R7_trust$country==16] <- "Malawi"
R7_trust$country_name[R7_trust$country==17] <- "Mali"
R7_trust$country_name[R7_trust$country==18] <- "Mauritius"
R7_trust$country_name[R7_trust$country==19] <- "Morocco"
R7_trust$country_name[R7_trust$country==20] <- "Mozambique"
R7_trust$country_name[R7_trust$country==21] <- "Namibia"
R7_trust$country_name[R7_trust$country==22] <- "Niger"
R7_trust$country_name[R7_trust$country==23] <- "Nigeria"
R7_trust$country_name[R7_trust$country==24] <- "São Tomé and Príncipe"
R7_trust$country_name[R7_trust$country==25] <- "Senegal"
R7_trust$country_name[R7_trust$country==26] <- "Sierra Leone"
R7_trust$country_name[R7_trust$country==27] <- "South Africa"
R7_trust$country_name[R7_trust$country==28] <- "Sudan"
R7_trust$country_name[R7_trust$country==29] <- "Tanzania"
R7_trust$country_name[R7_trust$country==30] <- "Togo"
R7_trust$country_name[R7_trust$country==31] <- "Tunisia"
R7_trust$country_name[R7_trust$country==32] <- "Uganda"
R7_trust$country_name[R7_trust$country==33] <- "Zambia"
R7_trust$country_name[R7_trust$country==34] <- "Zimbabwe"
```


```{r}
R2_trust_country_name <-
  R2_trust |>
  select(LG_trust:country_name)

R7_trust_country_name <-
  R7_trust |>
  select(LG_trust:country_name)

```

```{r}
all_rounds_country_name <- 
  bind_rows(R2_trust_country_name, R7_trust_country_name)
```

```{r}
library(dplyr)

all_rounds <-
dplyr::select(all_rounds_country_name, country_name, round, LG_trust, TL_trust)
```

```{r}
library(tidyverse)

all_rounds <-
  all_rounds |>
  filter(country_name %in% c("Botswana", "Ghana", "Lesotho", "Malawi", "Mali", "Namibia", "Nigeria", "South Africa", "Tanzania", "Uganda", "Zambia", "Zimbabwe", "Kenya", "Senegal")) 

all_rounds_2_levels <-
  all_rounds |>
  mutate(LG_trust_2levels = case_when(LG_trust <2~ 0,
                                      LG_trust %in% c(2,3) ~ 1,
                                      TRUE ~ NA_real_)) |>
  mutate(TL_trust_2levels = case_when(TL_trust <2~ 0,
                                      TL_trust %in% c(2,3) ~ 1,
                                      TRUE ~ NA_real_))

all_rounds_2_levels <-
  all_rounds_2_levels |>
  group_by(round, country_name) |>
  summarize(avg_LG_trust = mean(LG_trust_2levels, na.rm = TRUE), avg_TL_trust = mean(TL_trust_2levels, na.rm = TRUE)) |>
  pivot_wider(names_from = round, values_from = c("avg_LG_trust", "avg_TL_trust")) |>
  mutate(diff_LG_trust = `avg_LG_trust_r7` - `avg_LG_trust_r2`) |>
  mutate(diff_TL_trust = `avg_TL_trust_r7` - `avg_TL_trust_r2`) 
  
         
#all_rounds$LG_trust_3levels <- all_rounds$LG_trust       
#all_rounds$LG_trust_3levels[all_rounds$LG_trust>1] <- 
  
```
```{r}
plot_all_rounds_2_levels <-
  all_rounds_2_levels |>
  ggplot(aes(x = diff_LG_trust, y = diff_TL_trust, color = country_name)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Change in citizens' trust in LG between R2 and R7", y = "Change in citizens' trust in TL between R2 and R7", title = "Relationships between citizens' trust in local government and traditional leaders", caption = "Source: Afrobarometer")

plot_all_rounds_2_levels
```

## Interpretation of the graph 
I compared Afrobaromter survey Round 2 and Round 7. In both rounds, Afrobarometer asked the following questions: How much do you trust your local government council? How much do you trust your traditional leaders? The answers are: 0 (not at all), 1 (just a little), 2 (somewhat), 3(a lot).

In both questions, I compared the proportion of the respondents who answered either 2 (somewhat) and 3 (a lot) in Round 2 and Round 7, as shown in 'all_rounds_2_levels.' The plot shows that, in most countries, the more citizens trust in local government, the more they trust in traditional leaders. However, only in Uganda, the less citizens trust in local government, the more they trust in traditional leaders.

At this point, I assume that the difference between Uganda and other countries is the level of democracy. My hypothesis is, in more democratic countries in Sub-Saharan Africa, people's trust in local government and their trust in traditional authorities correlate positively, and in semi-authoritarian countries like Uganda, people's trust in local government and their trust in traditional authorities have negative correlation. I will eventually combine this data from Afrobaromter with Polity to see if the level of democracy is related to the relationship between citizens' trust in local government and their trust in traditional leaders. 


## Adding labels besides the points 

```{r}
plot_all_rounds_2_levels <-
  all_rounds_2_levels |>
  ggplot(aes(x = diff_LG_trust, y = diff_TL_trust, color = country_name)) +
  geom_point() +
  geom_text(aes(label = country_name)) +
  geom_smooth(method = "lm") +
  labs(x = "Change in citizens' trust in LG between R2 and R7", y = "Change in citizens' trust in TL between R2 and R7", title = "Relationships between citizens' trust in local government and traditional leaders", caption = "Source: Afrobarometer")

plot_all_rounds_2_levels
```





