---
title: "Gov 50 Final Project"
author: "Wakiko Ohira"
description: "My final project"
output:
  distill::distill_article:
    self_contained: false
---
```{r}
load("/Users/wakiko/Mac Google Drive/Harvard/Courses/Gov 50_Blackwell/afrobarometer2016.RData")
```

```{r}
library(haven)
round8 <- read_sav("data/afrobarometer_release-dataset_merge-34ctry_r8_en_2023-03-01.sav")
round2 <- read_sav("data/merged_r2_data.sav")
```

```{r}
#remotes::install_github("xmarquez/democracyData")
library(democracyData)
polity <- democracyData::polity5
```


## Project thoughts

I this study, I plan to examine the relationship between local citizens' trust in local government and their trust in traditional authorities in Sub-Saharan Africa. Traditional authorities, such as kingdoms and chiefdoms, are essential actors in local governance, and their roles vary from land allocation, customary arbitration, and provision of local public goods and services. In my previous study, I qualitatively examined the case of Uganda. In Uganda, the less citizens trust in local government, the more they trust in traditional authorities. My qualitative analysis showed that, because the central government instrumentalized local governments for the purpose of power consolidation, it greatly undermined local governments' capability to provide public goods and services. Local citizens are disappointed with both the central government and local governments, and their expectations of the kingdoms increased to be an alternative player in local governance. Using this qualitative study as a case, I hypothesize that, in more democratic countries in Sub-Saharan Africa, people's trust in local government and their trust in traditional authorities correlate positively, and in semi-authoritarian countries like Uganda, people's trust in local government and their trust in traditional authorities have negative correlation. I use the data from Afrobarometer (Round 2 and Round 8) to examine how much people's trust in local government increased or decreased over the past 20 years. I do the same analysis for how much people's trust in traditional authorities increased or decreased over the past 20 years. I conduct these analysis both at the individual level and the country level. Then, I combine the results with the data from polity, which shows the level of democracy, to test the hypothesis. 
